---
title: |
    \vspace{-2em}Homework assignment 1
subtitle: "KINESIOL 1E03 - Motor control and learning"
author: |
    \textcolor{maroon}{\textbf{Due date: Sept 17 2021 by 23:59 EST}}
output: hrbrthemes::ipsum_pdf
header-includes:
    \usepackage[sfdefault,condensed]{roboto}
    \usepackage[T1]{fontenc}
    \setlength{\headheight}{38.5pt}
    \usepackage{xcolor}
    \usepackage{float}
    \usepackage{fancyhdr}
    \pagestyle{fancy}
    \fancypagestyle{plain}{\pagestyle{fancy}}
    \fancyhead[L]{\includegraphics[width=2in,height=2in]{../../outline/mackin-left-color.png}}
    \fancyhead[R]{Assignment 1 instructions (Fall 2021)}
    \definecolor{maroon}{HTML}{7a003c}
mainfont: RobotoCondensed
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  dev = "cairo_pdf")
```

```{r include=FALSE}
# libraries
library(tidyverse)
library(kableExtra)

# load data
hw_data <- readr::read_csv("2021-09-16_assignment-1-data.csv")
```

# Questions

1. When it comes to measurement, three important concepts are *objectivity*, *sensitivity*, *reliability*, and *validity*. Define each of these terms (1 sentence per definition). \textcolor{maroon}{\textbf{[4 marks]}}

2. Using the data below, what is each person's:
    a) mean constant error? \textcolor{maroon}{\textbf{[1 mark]}}
    b) mean absolute error? \textcolor{maroon}{\textbf{[1 mark]}}
    c) mean variable error? \textcolor{maroon}{\textbf{[1 mark]}}
    d) mean absolute constant error? \textcolor{maroon}{\textbf{[1 mark]}}

```{r data-table, echo=FALSE}
kableExtra::kbl(
    hw_data,
    booktabs = TRUE,
    col.names = c("Trial",
                  "Person",
                  "Goal time",
                  "Response time")
) %>%
    kable_styling(position = "center",
                  latex_options = "HOLD_position") %>% 
    row_spec(0, bold = TRUE)
```

3. Can a person's constant error ever be greater in magnitude than their absolute error? In your answer be sure to explain why or why not? \textcolor{maroon}{\textbf{[2 marks]}}

# Submission guidelines

Your answers to the homework assignment questions should be typed and submitted via Avenue as a **PDF** file. Late assignments will be penalized 20% per day.

The file you submit must include your last name, first initial, and student ID using the following format: `a1_last-initial_ID.pdf`. For instance, I would submit an assignment named: `a1_carter-m_3351871.pdf`. Files submitted in the wrong format (e.g., Microsoft Turd's `.docx`) **will not be marked**.

Be sure to submit your file to the correct folder. Files submitted to the wrong folder **will not be marked**. If you need to resubmit your file to the correct folder after the due date, it will be considered late.
